---
title: "guncontrol"
author: "Gage Clawson"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This: I'm Gage and I'm updating this markdown file. 



```{r}
library(tidyverse)

gc_df <- read_csv("gc_df.csv")

```


We are asking: Is there a significant difference in reccomended gun control action for male and female respondents (should guns be easier, harder, or the same difficulty to get). 

Excellent question!! I am very interested in the results. 

Gage: data wrangling and counts

```{r}

get_guns <- gc_df %>%
  filter(make_get_guns != "NA", gender != "NA") %>%
  count(gender, make_get_guns) %>%
  spread(make_get_guns, n) %>%
  select(-gender) 

rownames(get_guns) <- c("Female", "Male")
  
#menaretrash



```
Hi my name is Gracie and I will do a chi-square for independence! Hooray!

Is there a significant assiciation between sex and opion on whether guns should be more difficult, easier, or the same difficulty to get. 

```{r}
#lets look at the actual proportions

guns_prop <- prop.table(as.matrix(get_guns), 1)

#run a chi-square test for independence 

guns_x2 <- chisq.test(get_guns)

guns_x2
```
Reccomended Government action on gun access differed significantly between male (n=x) and female (n=y) respondents. ($\chi^2$(`r guns_x2$paramenter`) = , p < 0.001). Notably, a much higher proportion (60%) of female respindents reccomend making it more difficult to get guns, compared to 40% of men. AKA #menaretrash

in console: guns_x2#stdres gives you which ones are more different than expected. usually 2 or -2 is within reason. 


